Timeliness of security updates for Android

### 2014-08-06 securityupdates.tex
Add that avo is contribution
Clarify what root equivalent means

The contributions of this paper are:
\begin{itemize}
 \item We quantify the vulnerability of Android to root equivalent vulnerabilities.
 \item We characterise the Android update ecosystem.
 \item We measure the security of Android according to three metrics and compare different manufacturers. and device models to allow consumers to differentiate between them based on security.
 \item We investigate the time-lines of vulnerabilities in Android.
 \item We provide models of how the distribution of Android versions changes allowing future version distributions to be predicted.
 \item We propose methods which could be used to improve the situation in future.
\end{itemize}

@@

\subsection{Root exploits}
We compiled a list of root exploit vulnerabilities for Android containing information on when they were known about, what versions they affected and which versions fixed the problem.
We only looked for \emph{root equivalent} exploits which did not require USB debugging to exploit.
\emph{Root equivalent} means that it grants privileges equivalent in scope to root which can then be used to gain root.
Some phones can be `rooted' by enabling USB debugging and using the special privileges of the adb shell to root the device but only \daAdbEnabledPerc\ of devices have USB debugging enabled.
This is not something that applications running on the phone can exploit to break compartmentalisation and so we do not include those exploits.
Unfortunately many published exploits use adb for convenience and so determining whether that is necessary to exploit the vulnerability can be difficult.
Some exploits which grant root are not traditional kernel exploits, for example the discovery of flaws in the verification of signatures on Android applications in February 2013~\cite{Forristal2013} meant that applications could pretend to be signed with system keys and hence gain root equivalent privileges.
On some versions of Android (below 4.1) they could use known system to root escalation mechanisms but on all versions they have a greatly increased attack area for further privilege escalation and also have the ability to control all user internet traffic (via VPNs), brick the phone, remove and install apps, steal user credentials, read the screen, make and receive calls.

>>>>

The contributions of this paper are:
\begin{itemize}
 \item We quantify the vulnerability of Android to root equivalent vulnerabilities.
 \item We characterise the Android update ecosystem.
 \item We collate information on vulnerabilities which affect Android.
 \item We measure the security of Android according to three metrics and compare different manufacturers. and device models to allow consumers to differentiate between them based on security.
 \item We investigate the time-lines of vulnerabilities in Android.
 \item We provide models of how the distribution of Android versions changes allowing future version distributions to be predicted.
 \item We propose methods which could be used to improve the situation in future.
\end{itemize}

@@

\subsection{Root exploits}
We compiled a list of root exploit vulnerabilities for Android containing information on when they were known about, what versions they affected and which versions fixed the problem.
We only looked for \emph{root equivalent} exploits which did not require USB debugging to exploit.
\emph{Root equivalent} means that it grants privileges equivalent in scope to root which can then either be used to gain root or provide sufficiently many permissions as to be as bad as root.
Some phones can be `rooted' by enabling USB debugging and using the special privileges of the adb shell to root the device but only \daAdbEnabledPerc\ of devices have USB debugging enabled.
This is not something that applications running on the phone can exploit to break compartmentalisation and so we do not include those exploits.
Unfortunately many published exploits use adb for convenience and so determining whether that is necessary to exploit the vulnerability can be difficult.
Some exploits which grant root are not traditional kernel exploits, for example the discovery of flaws in the verification of signatures on Android applications in February 2013~\cite{Forristal2013} meant that applications could pretend to be signed with system keys and hence gain root equivalent privileges.
On some versions of Android (below 4.1) they could use known system to root escalation mechanisms but on all versions they have a greatly increased attack area for further privilege escalation and also have the ability to control all user internet traffic (via VPNs), brick the phone, remove and install apps, steal user credentials, read the screen, make and receive calls.
